---
title: "Mod 15 Challenge"
output: html_document
---

** Deliverable 1**
```{r}
library(dplyr)
```
### Import Data and Create Table
```{r}
mechacar_table <- read.csv(file='MechaCar_mpg.csv')
```
### Perform linear regression to predict mpg using all six variables
```{r}
lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle +ground_clearance + AWD, data=mechacar_table)
```
# Determine p-value and r-square value
```{r}
my_summary <- summary(lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle +ground_clearance + AWD, data=mechacar_table)) 
```
```{r}
my_summary
```

```
The p-value is 0.0000000000535 so our null hypothesis can be rejected.
The R-squared value is: 0.7149 which indicates a postive correlation between our variables.
```

**Deliverable 2**
### Import Data and Create Table
```{r}
suspension_table <- read.csv(file='Suspension_Coil.csv', check.names = F, stringsAsFactors = F)
```
### Create summary dataframe
```{r}
total_summary <- suspension_table %>% group_by() %>% summarize(Mean=mean(PSI), Median=median(PSI), Variance = var(PSI), SD = sd(PSI),.groups="keep")
```
# view table
```{r}
summary(total_summary)
```

# Create dataframe to group each manufacturing lot 
```{r}
lot_summary <- group_by(suspension_table, Manufacturing_Lot)
summarize(lot, mean(PSI), median(PSI), var(PSI), sd(PSI))
```
# Deliverable 3

# Determine if the PSI accross all lots is statistically different from the population mean of 1500 pounds per square inch

# Create data frame for PSI equal to 1500 psi
```{r}
t.test(suspension_table$PSI,mu=1500)
```
```{r}
t.test(subset(suspension_table$PSI,suspension_table$Manufacturing_Lot=="Lot1"),mu=1500)
```
```{r}
t.test(subset(suspension_table$PSI,suspension_table$Manufacturing_Lot=="Lot2"),mu=1500)
```
```{r}
t.test(subset(suspension_table$PSI,suspension_table$Manufacturing_Lot=="Lot3"),mu=1500)
```


